---
title: "p8105_hw6_yx2858"
author: "Yueyi Xu"
date: "2023-11-28"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(broom)
library(boot)
library(dplyr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```



# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

### Create a bootstrap sample function

```{r}
set.seed(1)
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

### Create 5000 bootstrap samples

```{r}
boot_strap_df =
  weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, ~lm(tmax ~ tmin + prcp, data = .x)),
    beta = map(models, broom::glance),
    r2 = map(models, broom::tidy)
  ) |>
  unnest(beta, r2) |>
  dplyr::select(.id, term, estimate, r.squared) |>
  pivot_wider(names_from = term, values_from = estimate) |>
  rename(
    beta_0 = '(Intercept)',
    beta_1 = tmin,
    beta_2 = prcp
  )
```

### Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2

```{r}
r_s = 
  boot_strap_df |>
  select(r.squared) |>
  summarize(
    ci_low = quantile(r.squared, 0.025),
    ci_upp = quantile(r.squared, 0.975)
  )
```

print in table:

```{r}
r_s |>
  knitr::kable()
```

### Plot the distribution of r^2 estimate

```{r}
boot_strap_df |>
  select(r.squared) |>
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(
    title = "Distribution of r-squared estimates",
    x = "r-squared estimates",
    y = "Density",
    subtitle = "5000 bootstrap samples"
  )
```

Comment:
The distribution of the r-squared plot is approximately normal and slightly skewed to the left with a peak around and slightly higher to 0.92, indicating the majority of the bootstrap samples are about the value of 0.92 or close to this value.

### Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for $log(\widehat{\beta_1}*\widehat{\beta_2})$

```{r}
logbeta = 
  boot_strap_df |>
  mutate(log = log(beta_1 * beta_2)) |>
  drop_na()

log_beta1_beta2 =
  logbeta |>
  select(log) |>
  summarize(
    ci_low = quantile(log, 0.025),
    ci_high = quantile(log, 0.975)
  )
```

print in table:

```{r}
log_beta1_beta2 |>
  knitr::kable()
```

### Plot the distribution of $log(\widehat{\beta_1}*\widehat{\beta_2})$ estimate

```{r}
logbeta |>
  select(log) |>
  ggplot(aes(x = log)) +
  geom_density() +
  labs(
    title = "Distribution of log(B1+B2) estimates",
    x = "log(B1+B2) estimates",
    y = "density",
    subtitle = "5000 bootstrap samples"
  )
```

Comment:
The distribution of the log(B1+B2) plot is skewed to left with a peak around -5.5, indicating the majority of the bootstrap samples are about the values of -5.5 or close to this value.


# Problem 3

### Import data

```{r}
birthwt_df = 
  read_csv("birthweight.csv")
```

### Clean, tidy the data

```{r}
birthwt_clean_df =
  birthwt_df |>
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) |>
  janitor::clean_names() |>
  select(bwt, everything())
```

### Check for missing value

```{r}
sum(is.na(birthwt_clean_df))
```

There is no missing value in the tidified dataset.

### Propose a regression model for birthweight

```{r}
birthwt_mlr = lm(bwt ~., data = birthwt_clean_df)

birthwt_mlr |>
  broom::tidy() |>
  knitr::kable()
```

The above MLR is a regression model for birthweight. Each variable in the dataset is considered as a predictor of the regression model for birthweight.

### Plot of model residuals against fitted values

```{r}
birthwt_clean_df |>
  add_predictions(birthwt_mlr) |>
  add_residuals(birthwt_mlr) |>
  ggplot(aes(x = pred, y = resid)) +
  geom_smooth(method = "lm") +
  geom_point() +
  labs(
    title = "Residuals against Fitted Values",
    x = "Fitted Values",
    y = "Residuals"
  )
```

From the plot of the residuals against fitted value, the slop is 0, indicating there is no linear association between residuals against fitted values.

### Compare the model to two others: One using length at birth and gestational age as predictors (main effects only), One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
cv_df = 
  crossv_mc(birthwt_clean_df, 100) |>
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

```{r}
cv_df |>
  mutate(
    my_model_0 = map(train, ~ lm(bwt ~ ., data = .x)),
    model_1 = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(train, ~ lm(bwt ~ bhead * blength * babysex, data = .x))
  ) |>
  mutate(
    rmse_my_model_0 = map2_dbl(my_model_0, test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y))
  ) |>
  select(starts_with("rmse")) |>
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |>
  mutate(
    model = fct_inorder(model)
  ) |>
  ggplot(aes(x = model, y = rmse)) +
  geom_violin(aes(fill = model)) +
  labs(
    title = "Model against Root Mean Squared Error",
    x = "Model",
    y = "Root Mean Squared Error"
  )
```

From the plot of models against root mean squared error, my model has the lowest root squared error while model_1 using length at birth and gestational age as predictors has the highest root mean squared error, followed by model_2 using head circumference, length, sex, and all interactions (slightly lower than model_1 but higher than my model).





  




